Automated Formal Verification of Stand-alone Solar Photovoltaic Systems

### 2019-07-12 Tex/elsevier/reply Solar Energy JULY 2019.tex
revised comment (1)
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\begin{resposta} 
We thank the kind comment provided by this reviewer. Indeed, it summarizes what was intended to be done with this manuscript. In addition, we should highlight that the main focus was at the validation process of the solar PV system, instead of the mathematical modelling that was investigated in prior studies over the last two decades. This information was carefully included at the revised Abstract, Introduction and at the Conclusion sections, because we concluded that was not clear in the previous version of the paper.

Regarding the Figure 2, we did as highlighted by the reviewer. Moreover, we did the same to voltage V in order to keep the same standard.

>>>>

\begin{resposta} 
We thank the reviewer fot this insightful comment. Indeed, it summarizes what was intended to be studied in this manuscript. Additionally, we emphasize that the main focus of our study relies on the validation process of solar PV systems instead of the mathematical modelling, which was already investigated by prior studies over the last two decades; this particular information was carefully included in the revised abstract, introduction and conclusion sections since we concluded that it was unclear in the previous version of our manuscript. Regarding Figure 2, we fixed it as indicated by the reviewer. Moreover, we applied the same procedure to voltage V, in order to keep consistency throughout our manuscript.
